---
title: "R Notebook"
output: html_notebook
---
# INSTALL PACKAGES
```{r}
#install.packages ("tidyverse", dependencies = TRUE)
#install.packages("ggthemes", dependencies = TRUE)

```

#LOAD PACKAGES
```{r}
library(tidyverse)
library(ggthemes)
```
# IMPORT DATA
```{r}
exp1 = read_csv("exp1.csv")
nrow(exp1)
ncol(exp1)
colnames (exp1)
hist(exp1$rt)
```

#TIDYVERSE DATA
  #use this to sort through your data so you can filter for conditions
```{r}
condition_data = exp1 %>% select(subject, rt, typeoftrial, trialcondition, correct) %>% filter(typeoftrial == "picture" & trialcondition %in% c("Heavy_Normal", "Light_Smashed", "Heavy_Smashed", "Light_Normal"))
#exp1 %>% select (dataset, correct, typeoftrial) %>% filter(typeoftrial=="picture" & correct %in% c(1))
```

#SUMMARIZE IN TIDYVERSE
  #use this to find descriptive statistics
```{r}
condition_data %>% summarise(mean_rt = mean(rt), sd_rt = sd(rt), mean_acc = mean(correct))
```
#GROUPING DATA
  #we want to look at descriptive statoistics within each condition so we can use grouping to do this
```{r}
means = condition_data %>% group_by(trialcondition) %>% summarise(mean_rt = mean(rt), sd_rt = sd(rt), mean_acc = mean(correct))
```

#PLOTTING OUR DATA
  #we do this using ggplot

#BASIC HISTOGRAM
  #first we rold it which data to use
  #aes stands for aesthetics, since it is a histogram we only specify x axis
  #next we told it what type of plot and then label our axes and title
  #can also change theme if you want
```{r}
library(ggplot2)
library(ggthemes)
condition_data %>% ggplot(aes(x=rt)) +
  geom_histogram() + 
  xlab ("RT(in milliseconds)")+ 
  ylab ("Count")+ 
  ggtitle("Histogram of RT")

#modify histogram
condition_data %>% filter (rt<25000) %>% ggplot(aes(x=rt)) +
  geom_histogram(binwidth = 1000, fill = "red", color = "black", position = "identity") + theme_solarized() +
  xlab ("RT(in milliseconds)")+ 
  ylab ("Count")+ 
  ggtitle("Histogram of RT")

```
#TYPES OF PLOTS
  #density plots: geom_density()
  #scatterplots: geom_point()
  #bar plots: grom_bar()
  #line plots: geom_line()
  #boxplots: geom_boxplot()
  
#BAR GRAPHS
```{r}
means %>% ggplot(aes(x = trialcondition, y = mean_rt)) + geom_bar (stat = "identity", fill = "gold", color = "purple") + theme_fivethirtyeight() + xlab("RT (in milliseconds)") + ylab ("Count") + ggtitle ("Barplot of RT")
```

#MODIFIED CSV
  #saving a modified csv
    write_csv(name, "new name")
#NEW DATA PRACTICE EXCERCISE 1

```{r}
df = read_csv("relatedness_exp.csv")
part_df = df %>% select(ID, Type, pathlength, RT) %>% filter(Type == "Related" & pathlength %in% c(1,2))
 mean_all = df %>% summarise(mean_all = mean(RT))
mean_part = part_df %>% summarise(mean_part = mean(RT))
mean_ID = df %>% group_by(ID) %>% summarise(mean_ID = mean(RT))

```

    

  

